Moment Constraints Make Learning Latent-Variable Models Easier

### 2014-01-31 doc/icml2014/directed.tex
Finish approach figure
Added bottleneck outlines for all graphs

\begin{figure}
  \centering
  \input{figures/grid.tikz}
  \caption{A directed grid model.\todo{Annotate features}}
  \label{fig:grid}
\end{figure}

@@

\begin{lemma}(Canonical form) 
  \label{lem:reduction}
  Every directed graphical model can be transformed into one in which
  the observed variables are leaves with exactly one parent.
\end{lemma}
\begin{proof}
  \begin{figure}
    \label{fig:reduction}
    \centering
    \subimport{figures/}{reduction.tikz}
    \caption{Reduction to canonical form.}
  \end{figure}

  Let $x$ be an observed variable with parents $h_1, \cdots, h_p$ and
  children $h_{p+1}, \cdots, h_c$. Replace $x$ with a phantom hidden
  variable $h_x$, and make $x$ the child of $h_x$ (\figureref{reduction}). The domain of $h_x$
  has the same as $x$, and $\mOpp{x}{h_x} = I$.

  The parameters for $h_x$ are the same as $x$.
\end{proof}

>>>>

\begin{figure}
  \centering
  \input{figures/grid-outline.tikz}
  \caption{A directed grid model.}
  \label{fig:grid}
\end{figure}

@@

\begin{lemma}(Canonical form) 
  \label{lem:reduction}
Every directed graphical model can be transformed into one in which
  the observed variables are leaves with exactly one parent. 
There is a one-to-one correspondence between the parameters of this
  transformed model and the original one.
\end{lemma}
\begin{proof}
  \begin{figure}
    \centering
    \subimport{figures/}{reduction.tikz}
    \caption{Reduction to canonical form.}
    \label{fig:reduction}
  \end{figure}

  %\providecommand{\hp}{\ensuremath{h_{\textrm{phantom}}}}
  \providecommand{\hp}{\ensuremath{h_p}}

  Let $x_v$ be an observed variable with parents $P$ and children $C$.
  Consider the following transformation.
  Replace $x_v$ with a phantom hidden variable \hp with the same 
  domain\footnote{Though we have assumed that all hidden variables share the
      same domain, $[k]$, our work generalizes to hidden domains of
      arbitrary sizes, provided \assumptionref{full-rank-plus} holds.},
  parents $P$ and children $C \union \{x_{v_1}, x_{v_2}, x_{v_3}\}$,
  where $x_{v_1},x_{v_2},x_{v_3}$ are three copies of $x$
  (\figureref{reduction}). Also, set $\mOpp{v}{p} = I$.

  Then, there is a one-to-one correspondence between every value of
  $\hp$ and $x_v$. Consequently, for any clique $\sC \contains \hp$, the
  parameters in the original graphical model can be obtained by
  substituting $\hp$ with $x_v$.
\end{proof}
